Himalayan Expeditions Success Analysis 

### 2024-04-13 paper/paper.qmd
Cleaning information added to the appendix

@@

>>>>

(Plot the variables)

@@

## Cleaning
For the analysis data, the cleaning steps we took were:

1. Initial merging: I first merge the raw data from the `expeditions` and `members` datasets based on a common identifier, `expedition_id`, to consolidate information about expedition participants.

2. Column selection and renaming: Irrelevant columns are removed from the merged dataset, and the remaining columns (`peak_id.x`, `season.x`, `sex`, `age`, `success`, `solo`, `died`) are selected for further analysis. Additionally, column `peak_id.x` is renamed to `peak_id`.

3. Secondary merging: The cleaned `expeditions` dataset is merged with the `peaks` dataset based on a common identifier, `peak_id`, to incorporate information about the height of each peak climbed during expeditions.

4. Filtering out incomplete data: Rows with missing values for key variables such as `sex` or `age` are filtered out to ensure the integrity of the dataset.

5. Final dataset creation: The resulting dataset is further refined to include only relevant columns (`peak_id`, `height_metres`, `season.x`, `sex`, `age`, `success`, `solo`, `died`). Some column names are adjusted for clarity, such as `season.x` being renamed to `seasons`, and `height_metres` being renamed to `height`.
